CommonMind Consortium: DLPFC

### 2021-01-15 combined_analysis/combine_all_DLPFC.Rmd
For public release

## t-statistics for CASKIN1
```{r CASKIN1}
 df_two['ENSG00000167971',]  %>% kable(caption="t-statistics for CASKIN1", row.names=FALSE) %>% kable_styling(full_width=FALSE)
 df_two['ENSG00000163634',]  %>% kable(caption="t-statistics for CASKIN1", row.names=FALSE) %>% kable_styling(full_width=FALSE)
```

>>>>

## t-statistics for CASKIN1
```{r CASKIN1}
 df_two['ENSG00000167971',]  %>% kable(caption="t-statistics for CASKIN1", row.names=FALSE) %>% kable_styling(full_width=FALSE)
```
